Latentcor: An R Package for Latent Correlation Estimation

### 2021-05-31 paper/paper.Rmd
Create reference table.

The R package *latentcor* provides estimation for latent correlation with mixed data types (continuous, binary, truncated and ternary). Comparing to *MixedCCA*, which estimates latent correlation for canonical correlation analysis, our new package provides a standalone version for latent correlation estimation. Also we add new functionality for latent correlation between ternary/continous, ternary/binary, ternary/truncated and ternary/ternary cases.
Compare to MixedCCA, standalone, new functionality, memory footprint.

# Statement of need
No package deal with latent correlation across mixed data type.

# Usage
 Create a table
 type of variable (reference to papers)
 Definition for Kendall tau.
 Describe the theorem states expected value of kendall tau = F(r). refer to table for reference of formula.
 A sentence to describe two methods: slow original vs interpolation.
 Table to show memory improvement compare to mixedCCA.
 Generate data for pairs.
 One example of original call, one for interpolation call.
# Citations

@@

# Acknowledgements

>>>>

The R package *latentcor* provides estimation for latent correlation with mixed data types (continuous, binary, truncated and ternary). Comparing to *MixedCCA*, which estimates latent correlation for canonical correlation analysis, our new package provides a standalone version for latent correlation estimation. Also we add new functionality for latent correlation between ternary/continous, ternary/binary, ternary/truncated and ternary/ternary cases.

Compare to MixedCCA, standalone, new functionality, memory footprint.

# Statement of need
Currently there is no standalone package dealing with latent correlation for mixed data type like we did in *latentcor*. The R package *stats* [@team2013r] have some functionality to calculate different type of correlations (Pearson, Kendall and Spearman). The R package *pcaPP* [@croux2013robust] provides a fast calculation for Kendall's \tau. The R package *MixedCCA* [@yoon2020sparse] have functionality for latent correlation estimation as an intermediate step for canonical correlation analysis on mixed data.
No package deal with latent correlation across mixed data type.

# Usage

 |Type | continuous | binary | truncated | ternary |
|-----|----------|
|continuous | @liu2009nonparanormal | @fan2017high | @yoon2020sparse | @quan2018rank |
|binary | @fan2017high | @fan2017high | @yoon2020sparse | @quan2018rank |
|truncated | @yoon2020sparse | @yoon2020sparse | @yoon2020sparse | This paper |
|ternary | @quan2018rank | @quan2018rank | This paper | @quan2018rank |

 Definition for Kendall tau.
 Describe the theorem states expected value of kendall tau = F(r). refer to table for reference of formula.
 A sentence to describe two methods: slow original vs interpolation.
 Table to show memory improvement compare to mixedCCA.
 Generate data for pairs.
 One example of original call, one for interpolation call.

@@

### 2021-05-31 paper/paper.tex
Create reference table.

\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Latentcor: An R Package for Latent Correlation Estimation},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Pandoc citation processing

@@

The R package \emph{latentcor} provides estimation for latent
correlation with mixed data types (continuous, binary, truncated and
ternary). Comparing to \emph{MixedCCA}, which estimates latent
correlation for canonical correlation analysis, our new package provides
a standalone version for latent correlation estimation. Also we add new
functionality for latent correlation between ternary/continous,
ternary/binary, ternary/truncated and ternary/ternary cases. Compare to
MixedCCA, standalone, new functionality, memory footprint.

@@

No package deal with latent correlation across mixed data type.

@@

Create a table type of variable (reference to papers) Definition for
Kendall tau. Describe the theorem states expected value of kendall tau =
F(r). refer to table for reference of formula. A sentence to describe
two methods: slow original vs interpolation. Table to show memory
improvement compare to mixedCCA. Generate data for pairs. One example of
original call, one for interpolation call. \# Citations

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

\hypertarget{references}{%
\section{References}\label{references}}

>>>>

\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Latentcor: An R Package for Latent Correlation Estimation},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

The R package \emph{latentcor} provides estimation for latent
correlation with mixed data types (continuous, binary, truncated and
ternary). Comparing to \emph{MixedCCA}, which estimates latent
correlation for canonical correlation analysis, our new package provides
a standalone version for latent correlation estimation. Also we add new
functionality for latent correlation between ternary/continous,
ternary/binary, ternary/truncated and ternary/ternary cases.

Compare to MixedCCA, standalone, new functionality, memory footprint.

@@

Currently there is no standalone package dealing with latent correlation
for mixed data type like we did in \emph{latentcor}. The R package
\emph{stats} (Team \& others, 2013) have some functionality to calculate
different type of correlations (Pearson, Kendall and Spearman). The R
package \emph{pcaPP} (Croux, Filzmoser, \& Fritz, 2013) provides a fast
calculation for Kendall's \tau. The R package \emph{MixedCCA} (Yoon,
Carroll, \& Gaynanova, 2020) have functionality for latent correlation
estimation as an intermediate step for canonical correlation analysis on
mixed data. No package deal with latent correlation across mixed data
type.

@@

Create a table

\begin{longtable}[]{@{}ll@{}}
\toprule
Type & continuous \\
\midrule
\endhead
continuous & (\textbf{davis2006reliable?}) \\
binary & (\textbf{dice1945measures?}) \\
truncated & (\textbf{dunne2002solutions?}) \\
ternary & (\textbf{bommert2020adjusted?}) \\
stabilityIntersectionGreedy & (\textbf{bommert2020adjusted?}) \\
stabilityIntersectionMBM & (\textbf{bommert2020adjusted?}) \\
stabilityIntersectionMean & (\textbf{bommert2020adjusted?}) \\
stabilityJaccard & (\textbf{jaccard1901etude?}) \\
stabilityKappa & (\textbf{carletta1996assessing?}) \\
stabilityLustgarten & (\textbf{lustgarten2009measuring?}) \\
stabilityNogueira & (\textbf{nogueira2018stability?}) \\
stabilityNovovicova & (\textbf{novovicova2009new?}) \\
stabilityOchiai & (\textbf{ochiai1957zoogeographic?}) \\
stabilityPhi & (\textbf{nogueira2016measuring?}) \\
stabilitySechidis & (\textbf{sechidis2020stability?}) \\
stabilitySomol & (\textbf{somol2008evaluating?}) \\
stabilityUnadjusted & (\textbf{bommert2020adjusted?}) \\
stabilityWald & (\textbf{wald2013stability?}) \\
stabilityYu & (\textbf{yu2012stable?}) \\
stabilityZucknick & (\textbf{zucknick2008comparing?}) \\
\bottomrule
\end{longtable}

type of variable (reference to papers) Definition for Kendall tau.
Describe the theorem states expected value of kendall tau = F(r). refer
to table for reference of formula. A sentence to describe two methods:
slow original vs interpolation. Table to show memory improvement compare
to mixedCCA. Generate data for pairs. One example of original call, one
for interpolation call.

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-croux2013robust}{}%
Croux, C., Filzmoser, P., \& Fritz, H. (2013). Robust sparse principal
component analysis. \emph{Technometrics}, \emph{55}(2), 202--214.

\leavevmode\hypertarget{ref-team2013r}{}%
Team, R. C., \& others. (2013). R: A language and environment for
statistical computing.

\leavevmode\hypertarget{ref-yoon2020sparse}{}%
Yoon, G., Carroll, R. J., \& Gaynanova, I. (2020). Sparse semiparametric
canonical correlation analysis for data of mixed types.
\emph{Biometrika}, \emph{107}(3), 609--625.

\end{CSLReferences}
